The ChEMBL database as Linked Open Data

### 2012-04-17 article.tex
Added statement of funding.
fix latex syntax and hide internal notes

NOTE: Full set of ChEMBL molecules have been created by querying molecule_dictionary table
NOTE: I have added extra triple for each molecule: <http://data.kasabi.com/dataset/chembl-rdf/13/molecule/m1> <http://www.w3.org/1999/02/22-rdf-syntax-ns#type> <http://rdf.farmbio.uu.se/chembl/onto/#Molecule> .
NOTE: Modified molecule compound structure can be queried here: https://wwwdev.ebi.ac.uk/chembl/sparql

@@

The following SPARQL query returns the 44,681 ChEMBL documents. This is 1 less than appears 
in ChEMBL 13 release notes, as it does not include doc_id -1, which refers to the 
unpublished dataset.

@@

Tim Hodson and Zach Beauvais of Kasabi and A. L\"ovgren at the at Uppsala Biomedical Centre at Uppsala University for their
support.

>>>>

%Mark Davies notes:
%NOTE: Full set of ChEMBL molecules have been created by querying molecule\_dictionary table
%NOTE: I have added extra triple for each molecule: <http://data.kasabi.com/dataset/chembl-rdf/13/molecule/m1> <http://www.w3.org/1999/02/22-rdf-syntax-ns#type> <http://rdf.farmbio.uu.se/chembl/onto/#Molecule> .
%NOTE: Modified molecule compound structure can be queried here: https://wwwdev.ebi.ac.uk/chembl/sparql

@@

The following SPARQL query returns the 44,681 ChEMBL documents. This is 1 less than appears 
in ChEMBL 13 release notes, as it does not include doc\_id -1, which refers to the 
unpublished dataset.

@@

Tim Hodson and Zach Beauvais of Kasabi and A. L\"ovgren at the at Uppsala Biomedical Centre at Uppsala University for their
support. OS acknowledges funding from the Swedish VR (2011-6129) and eSSENCE.
